---
title: "Alcohol vs Seat choice"
author: "Kathleen Castro"
date: "Spring, 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
Looking at the Fancy notch boxplot, we see 3 different types of people's seating. This includes the back, front, and middle. After giving a close analysis at this information, we can see that people seated in the back have a differing medium compared to the people sitting in the front. People sitting in the back seem to obtain more drinks compared to most people sitting in the front.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
  
Observing this data shows data on the medium of how many people have drinks when seated at the back. The median for the back is 4 while the front and middle range between 0 to 1.
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  
Observing the inferential test shows us that a small number under the P-value is within 0.000116. This data gives us the understanding where there was no difference of alcohol consumption between the front and the middle

```{r}
plot(TukeyHSD(model1))
```
  
The provided plot infers a difference between the alcohol consumed within the front-back and the middle-front. The data also hows how neither type crosses with each other of the back, middle, and front.

## Conclusions
  

