---
title: "Alcohol vs Seat choice"
author: "Kathleen Castro"
date: "Spring, 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
Looking at the Fancy notch boxplot, we see 3 different types of people's seating. This includes the back, front, and middle. After giving a close analysis at this information, we can see that people seated in the back have a differing medium compared to the people sitting in the front. People sitting in the back seem to obtain more drinks compared to most people sitting in the front.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
  
Observing this data shows data on the medium of how many people have drinks when seated at the back. The median for the back is 4 while the front and middle range between 0 to 1.
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  
Observing the inferential test shows us that a small number under the P-value is within 0.000116. This data gives us the understanding where there was no difference of alcohol consumption between the front and the middle

```{r}
plot(TukeyHSD(model1))
```
  
The provided plot infers a difference between the alcohol consumed within the front-back and the middle-front. The data also hows how neither type crosses with each other of the back, middle, and front.

## Conclusions
  
In conclusion, this data shows how the people located in the back consume more alcohol compared to people seated in the middle and the front. The first data graph gives us data on the different medians. People sitting in the back have a higher median of consuming drinks compared to other seating areas. The second data piece shows us the difference between the different types, which turns out to be a very small digit signifying that there is a small difference between the three types. The third data shows us a graph on how the previous data doesn't cross or intertwine with each other.